Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
paper: Add performance metrics and comment for wikitext

>>>>

\section{Performance by Model Architecture}
\label{sec:perf_by_model_arch}

\begin{figure}[h]
\includegraphics{sr-perf-by-model-architecture}
\centering
\caption{Validation Set Performance by Model Architecture on WikiText}
\end{figure}

Comparing each of the three models with 200 hidden units, 2 layers and
no dropout or embeddings, trained to five epochs in batches of 200 sentences at a
time, we see that the LSTM model generally outperforms all three on all metrics.
It has the lowest overall perplexity, highest METEOR score after five iterations
and highest overall naive accuracy, scoring roughly one half a percentage point
higher than the other two models.

\section{Performance by number of hidden layers}
\label{sec:perf_by_n_layers}

\begin{figure}[h]
\includegraphics{sr-perf-by-hidden-lstm}
\includegraphics{sr-perf-by-hidden-gru}
\includegraphics{sr-perf-by-hidden-rnn}
\centering
\caption{Validation Set Performance by number of Hidden Layers on WikiText}
\end{figure}

We measured differences in performance with both one and two hidden layers
on the RNN cell for each model architecture with 200 hidden units per cell, trained
to five epochs in batches of 200 sentences at a time.

In general, we find that increasing the number of hidden layers on the network
increases performance on all metrics, probably because the model is able to
encode more information from the training set in its layers recurrent layers.

We notice that in the Elman Network RNN training was generally unstable and
increasing the number of layers gave inconclusive results.

\section{Performance by number of hidden units}
\label{sec:perf_by_n_hidden}

\begin{figure}[h]
\includegraphics{sr-perf-by-hidden-units-lstm}
\includegraphics{sr-perf-by-hidden-units-gru}
\includegraphics{sr-perf-by-hidden-units-rnn}
\centering
\caption{Validation Set Performance by number of Hidden Units on WikiText}
\end{figure}

We measured differences in performance with 60, 90, 150 and 200 hidden units per
RNN cell for each model architecture with 1 RNN cell, trained
to five epochs in batches of 200 sentences at a time.

In general we found that like increasing the number of layers,
increasing the number of hidden units per layer can help with overall accuracy,
but not as much as increasing the number of layers does. In fact, having a fewer
number of hidden units may act as a regularizer which would help to prevent
overfitting and improve accuracy on the validation data.

\section{Performance by Dropout}
\label{sec:perf_by_dropout}

\begin{figure}[h]
\includegraphics{sr-perf-by-dropout-lstm}
\includegraphics{sr-perf-by-dropout-gru}
\includegraphics{sr-perf-by-dropout-rnn}
\centering
\caption{Validation Set Performance by Dropout Probability on WikiText}
\end{figure}

We measured differences in performance with dropout probabilities
0.0, 0.01, 0.05, 0.1, 0.2 per RNN cell for each model architecture with
1 RNN cell, 200 hidden units, trained to five epochs in batches of 200
sentences at a time.

For GRU cells, we find that small amounts of dropout (0.01-0.05) can act
as an effective regularizer and improve accuracy and ROUGE scores on unseen
data by a few tenths of a percentage point. For LSTM cells we find that
dropout did not assist all that much, indicating that perhaps those models were
not already starting to overfit by five epochs. For RNN cells, we observed
that again, training was quite unstable that it was difficult to observe what
difference, if any, dropout had on the metrics.

\section{Performance by Embedding Dimensions}
\label{sec:perf_by_embedding}

\begin{figure}[h]
\includegraphics{sr-perf-by-embedding-lstm}
\includegraphics{sr-perf-by-embedding-gru}
\includegraphics{sr-perf-by-embedding-rnn}
\centering
\caption{Validation Set Performance by Embedding Dimension on WikiText}
\end{figure}

We measured differences in performance with embedding sizes 0, 50,
100, 200 and 500 at the encoder layer for each model architecture with
1 RNN cell, 200 hidden units, trained to five epochs in batches of 200
sentences at a time.

On both LSTM and GRU models, any use of encoder embeddings noticably outperformed
one-hot encoding on almost all metrics, except METEOR for LSTMs. It seems to be
the case that the learned embeddings encoded useful information about the
non-temporally dependent relationships between words. For Elman RNN cells, we
again observed that because training was so unstable, embeddings did not
appear to make much of a difference to accuracy, even if they result in
much lower computational complexity.

\section{Performance by Shortlist Dimension}
\label{sec:perf_by_shortlist}

\begin{figure}[h]
\includegraphics{sr-perf-by-shortlist-lstm}
\includegraphics{sr-perf-by-shortlist-gru}
\includegraphics{sr-perf-by-shortlist-rnn}
\centering
\caption{Validation Set Performance by Shortlist Dimension on WikiText}
\end{figure}

We measured differences in performance with shortlist sizes 100, 1000, 5000, 1000
at the decoder layer for each model architecture with 1 RNN cell, 200 hidden units and
an input encoder embedding size of 500, trained to five epochs in batches of 200 sentences at a time.

On WikiText, note that the original corpus contained 28,755 words in its
dictionary and achieved accuracy scores of 0.921 for the LSTM, 0.918 for the GRU
and 0.911 for Elman RNN.

By contrast, shortlists for LSTM, GRU and Elman RNNs
achieve accuracy scores between 0.910 and to 0.911,
with larger shortlists marginally outperforming smaller
shortlists. This indicates that a large proportion of
the words being predicted on the non-shortlisted
models are likely to be very frequent words, meaning
that if we \emph{only} allow the network to predict
frequent words by shortlisting then we can still get
slightly worse but similar performance.

\section{Tied Weights}
\label{sec:perf_by_tiedweights}

\begin{figure}[h]
\includegraphics{sr-perf-by-model-tied-weights}
\centering
\caption{Validation Set Performance by Model on WikiText for Tied Weights}
\end{figure}

\section{Xavier Initialization}
\label{sec:perf_by_xavier_init}

\begin{figure}[h]
\includegraphics{sr-perf-by-model-xavier-init}
\centering
\caption{Validation Set Performance by Model on WikiText for Xavier Initialization}
\end{figure}

\section{Kaiming Initialization}
\label{sec:perf_by_kaiming_init}

\begin{figure}[h]
\includegraphics{sr-perf-by-model-kaiming-init}
\centering
\caption{Validation Set Performance by Model on WikiText for Xavier Initialization}
\end{figure}
